The Supervisionary proof-checking kernel

### 2021-10-11 paper/prisc-2022.tex
prisc-2022: fix some minor typos

This pattern of interaction between trusted and untrusted code via an ABI, wherein trusted code can read and modify the state of untrusted code, is common.
Hypervisors, the Secure World of Arm TrustZone, and virtual machines (in the Wasm sense) are structured in this way.
Call software designed in this pattern \deffont{supervisory software}.

@@

Nothing in principle stops us from extending Supervisionary's ABI with facilities for sockets, querying a hierarchical filesystem, and other similar system tasks.
In particular, given our use of Wasm, we could implement the Wasm System Interface---a POSIX-like interface for Wasm---transforming Supervisionary from a programmable proof-checker into a general-purpose virtual machine, capable of supporting a wide-range of programs.

>>>>

This pattern of interaction between trusted and untrusted code via an ABI, wherein trusted code can read and modify the state of untrusted code, is common.
Hypervisors, the Secure World of Arm TrustZone, and virtual machines (in the Wasm sense) are structured in this way.
We call software designed in this pattern \deffont{supervisory software}.

@@

Nothing in principle stops us from extending Supervisionary's ABI with facilities for sockets, querying a hierarchical filesystem, and other similar system tasks.
In particular, given our use of Wasm, we could implement the Wasm System Interface---a POSIX-like interface for Wasm---transforming Supervisionary from a programmable proof-checker into a general-purpose virtual machine, capable of supporting a wide range of programs.
